Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
boxplot update

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441,just-defects4j-issta2014}. 
A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is
corrected by adding code. Intuitivelly, the ability of techniques to
produce accurate diagnostic reports in those cases is poor since fault of omission
are non-executable statements which means that the execution information
cannot help locate the fault directly. A total of $59.7\%$ of the cases
in this dataset manifest fault of omission, which is a good indication of
difficulty\Sof{note to self: Improve the good indication of difficulty}.

@@

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

A fundamental issue of purely dynamic slicing techniques is the risk
of discarding faulty statements (see Section~\ref{sec:slicing}). This
research question evaluates the practical impact of this conceptual
issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
dynamic slicing captures at least one of the faulty statements among
the sliced files for different values of $k$. These numbers indicate
that in general \ds{} finds at least one faulty statement in the top
$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
is slightly improved for $91.2\%$ if we consider
the top $10$ of the highest-ranked faulty classes.
\Sof{Percebo o objectivo da tabela 3 mas não seria melhor arranjar
maneira de não precisar de repetir? Estes resultados estão na tabela 4}

\begin{table}[H]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$ using histograms over $\Delta{}C$ for
different values of $k$. Note that (1) the number of cases where
\sfl{}$^{k}$ outperforms \combpar{k} is very small compared and (2)
the number of cases \combpar{k} outperforms \sfl{}$^{k}$ is
significant and, as we increase the value of $k$, it increases (from
97 to 117 faults).

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.47\textwidth]{figures/double-boxplot.pdf}
		\caption{Boxplot of $\Delta{}C$.}
		\label{fig:boxplot}
\end{figure}
%
% \begin{figure}[h]
% 		\centering
% 		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
% 		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
% 		\label{fig:boxplot}
% \end{figure}

>>>>

As to quantify complexity of fault localization on this dataset, we
additionally counted the number of cases of ``fault of omission'', a
popular metric in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441,just-defects4j-issta2014}. 
A fault of omission occurs when
the program is buggy because some code is missing, i.e., a bug that is
corrected by adding code. Intuitivelly, the ability of techniques to
produce accurate diagnostic reports in those cases is poor since fault of omission
are non-executable statements which means that the execution information
cannot help locate the fault directly. A total of $59.7\%$ of the cases
in this dataset manifest fault of omission, which is a good indication of
difficulty\Sof{icse17 check}.

@@

\begin{table}[h]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

A fundamental issue of purely dynamic slicing techniques is the risk
of discarding faulty statements (see Section~\ref{sec:slicing}). This
research question evaluates the practical impact of this conceptual
issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
dynamic slicing captures at least one of the faulty statements among
the sliced files for different values of $k$. These numbers indicate
that in general \ds{} finds at least one faulty statement in the top
$5$ of the highest-ranked faulty classes ($87.3\%$ on average) which
is slightly improved for $91.2\%$ if we consider
the top $10$ of the highest-ranked faulty classes.

\begin{table}[h]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$ using histograms over $\Delta{}C$ for
different values of $k$. Note that (1) the number of cases where
\sfl{}$^{k}$ outperforms \combpar{k} is very small compared and (2)
the number of cases \combpar{k} outperforms \sfl{}$^{k}$ is
significant and, as we increase the value of $k$, it increases (from
$97$ to $117$ faults).

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.49\textwidth]{figures/boxplot.pdf}
		\caption{Boxplot of $\Delta{}C$.}
		\label{fig:boxplot}
\end{figure}
%
% \begin{figure}[h]
% 		\centering
% 		\includegraphics[width=0.42\textwidth]{figures/boxplot_all.pdf}
% 		\caption{Boxplot of $\Delta{}C$. \Sof{Considering the best cases and the \textbf{top-misses}}}
% 		\label{fig:boxplot}
% \end{figure}
